Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-20 krs-survey.tex
Minor update to the Soar/ACT-R paragraph

While classical cognitive systems like {\sc Soar} or {\sc ACT-R} have
declarative knowledge modules and have been recently used on service robots
(see {\sc ACT-R/E}~\cite{Kennedy2009} for instance), they are absent from this
survey because we could not find evidence in the litterature on possible
on-line manipulation of symbolic knowledge.

>>>>

While classical cognitive architectures like {\sc Soar} or {\sc ACT-R} have
declarative knowledge modules~\cite{Derbinsky2010} and have been recently used
on service robots (see {\sc ACT-R/E}~\cite{Kennedy2009} for instance), they are
also absent from this survey because we did not find much references in the
litterature on knowledge manipulation and representation applied to robotic
scenarii in these architectures.
